MP MetaAnalysis Monolinguals

### 2018-07-18 Paper_Analyses_monolinguals.Rmd
Cog_Sci_Talk_prep

---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31)

@@

@@

@@

@@

```{r MPtype_cond_lang}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )

>>>>

---
title: "MP MetaAnalysis Monolinguals"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31, infant_type == "typical")

@@

```{r PlotDistFamEffect_condition}

@@

```{r DistractorTypeAgeRangeSubset}

@@

```{r PlotDistOverlap_cond_age}

@@

```{r MPtype_cond_lang_age}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" )
